The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-10-02 paper/paper.Rmd
Move ecology and evolution paper back to paper folder

```{r scbi-simulation, out.width="100%", fig.cap="Comparison of root mean squared error of models for standard, permuted, and spatially cross-validated error estimates. The dotted lines show observed RMSE while the histograms show the null distribution of RMSE for 49 permutations under the null hypothesis of no competitor species identity effects. The colors indicate whether spatial cross-validation was used or not.", echo = FALSE}
include_graphics("simulation_results/2021-03-03_scbi_49_shuffles.pdf")
```

>>>>

```{r scbi-simulation, out.width="100%", fig.cap="Comparison of root mean squared error of models for standard, permuted, and spatially cross-validated error estimates. The dotted lines show observed RMSE while the histograms show the null distribution of RMSE for 49 permutations under the null hypothesis of no competitor species identity effects. The colors indicate whether spatial cross-validation was used or not.", echo = FALSE}
include_graphics("simulation_results/2021-03-03_scbi_49_shuffles.tiff")
```
